---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
dataFolder = "image_analysis/"

```

Comparing the flickers

```{r}
filename = "black_white_next/kitti.csv"
df = read.csv(paste(dataFolder,filename,sep = ""), check.names = FALSE)

plot(df$bw_b, col = "blue", type = "l",
     main = "Colored flickers: black, white, ..."
    )
points(df$bw_r, col="red", type="l")

# legend(15, max(df$red_top), legend=c("Sum of red", "Sum of blue"),
#       col=c("red", "blue"), cex=0.8)


plot(df$wb_r, col = "red", type = "l",
     main = "Colored flickers: white, black, ..."
    )
points(df$wb_b, col="blue", type="l")

```


Comparing the amount of blue in the top of the images (==background: sky, trees) vs the bottom (foreground: road).
Hypothesis: maybe backgrounds tend to be redder and foregrounds tend to be bluer?

```{r}
filename = "top_bottom_diff.csv"
df = read.csv(paste(dataFolder,filename,sep = ""), check.names = FALSE)

```

```{r}
plot(df$red_top, col = "red", type = "l",
     main = "Top of frames", ylim = c(min(df$blue_top)-100000, max(df$red_top) + 100000)
    )
points(df$blue_top, col="blue", type="l")
legend(15, max(df$red_top), legend=c("Sum of red", "Sum of blue"),
       col=c("red", "blue"), cex=0.8)

plot(df$red_bottom, col = "red", type = "l",
     main = "Bottom of frames", ylim = c(min(df$blue_bottom)-100000, max(df$red_bottom) + 100000)
    )
points(df$blue_bottom, col="blue", type="l")
legend(15, max(df$red_top), legend=c("Sum of red", "Sum of blue"),
       col=c("red", "blue"), cex=0.8)


plot(df$red_top, col = "red", type = "l", 
     main = "Red in frames, bottom vs top", ylim = c(min(df$red_top)-100000, max(df$red_bottom) + 100000)
    )
points(df$red_bottom, col="red", type="l", lty=2)
legend(15, max(df$red_top), legend=c("Red in top", "Red in bottom"),
       col=c("red", "red"), lty=1:2, cex=0.8)

plot(df$blue_top, col = "blue", type = "l", 
     main = "Blue in frames, bottom vs top", ylim = c(min(df$blue_bottom)-100000, max(df$blue_bottom) + 100000)
    )
points(df$blue_bottom, col="blue", type="l", lty=2)
legend(15, max(df$blue_top), legend=c("Blue in top", "Blue in bottom"),
       col=c("blue", "blue"), lty=1:2, cex=0.8)
```


Test if approaching objects become bluer/redder as result of atmospheric dispersion

```{r}
filename = "reds_blues.csv"
df = read.csv(paste(dataFolder,filename,sep = ""), check.names = FALSE)

```

```{r}

plot(df$red, col = "red", type = "l",
     main = "Approaching tree", ylim = c(min(df$red)-2, max(df$blue) + 2)
    )
points(df$blue, col="blue", type="l")
legend(8, 58, legend=c("Red average", "Blue average"),
       col=c("red", "blue"),  lty=c(1,1), cex=0.8)
```

Check if moving objects have more blues on their motion direction side and more red on the other side

```{r}
filename = "motion_half.csv"
df = read.csv(paste(dataFolder,filename,sep = ""), check.names = FALSE)

```

```{r}
plot(df$red_left, col = "red", type = "l",
     main = "Left of frames"#, ylim = c(min(df$blue_top)-100000, max(df$red_top) + 100000)
    )
points(df$blue_left, col="blue", type="l")
legend(8, 32, legend=c("Red Average", "Blue average"),
       col=c("red", "blue"), lty=c(1,1), cex=0.8)

plot(df$red_right, col = "red", type = "l",
     main = "Right of frames", ylim = c(min(df$red_right)-2, max(df$blue_right) + 2)
    )
points(df$blue_right, col="blue", type="l")
legend(8, 30, legend=c("Red Average", "Blue average"),
       col=c("red", "blue"), lty=c(1,1), cex=0.8)

```


Colors

```{r}
dataFolder = "results//bike_lines_fw//"
filename = "colors_average_20.csv"
df = read.csv(paste(dataFolder,filename,sep = ""), check.names = FALSE)

plot(x = df$red, type = "l", col = "red", ylab = "Average color values"
     #, ylim=c(0,10)
     )
points(x = df$green, type = "l", col = "green")
points(x = df$blue, type = "l", col = "blue")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.
